Entropy-SGD: Biasing Gradient Descent Into Wide Valleys

### 2017-01-25 doc/arxivize.tex
uploaded to arxiv

\documentclass[letterpaper]{article}
\usepackage{hyperref}
\hypersetup{
  pdfinfo={
    Title={Entropy-SGD: Biasing Gradient Descent Into Wide Valleysre},
    Author={Pratik Chaudhari, Anna Choromanska, Stefano Soatto, Yann LeCun},
    Keywords={deep learning, gradient descent, optimization, machine learning, neural networks}
  }
}
\usepackage{pdfpages}
\usepackage{grffile}

>>>>

\documentclass[letterpaper]{article}
\usepackage{hyperref}
\hypersetup{
  pdfinfo={
    Title={Entropy-SGD: Biasing Gradient Descent Into Wide Valleysre},
    Author={Pratik Chaudhari, Anna Choromanska, Stefano Soatto, Yann LeCun,Carlo Baldassi,Christian Borgs,Jennifer Chayes,Levent Sagun,Riccardo Zecchina},
    Keywords={deep learning, gradient descent, optimization, machine learning, neural networks,statistical physics, local entropy}
  }
}
\usepackage{pdfpages}
\usepackage{grffile}
